---
title: "Fatigue Assessment (MNH26) Variable Review"
date: "`r Sys.Date()`"
output:
  pdf_document:
    toc: true
    toc_depth: 3
    latex_engine: xelatex
    keep_tex: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE, out.width = "100%", fig.align = "center") 

library(tidyverse)

load("derived_data/df_ftg.rda")
load("derived_data/df_ftg_long.rda")

```

### Includes data from synapse last updated: {.unlisted .unnumbered}
### Pakistan : 2023-10-13 {.unlisted .unnumbered}
### Kenya : 2023-10-13 {.unlisted .unnumbered}
### Ghana : 2023-10-13 {.unlisted .unnumbered}
### Zambia : 2023-10-13 {.unlisted .unnumbered}
### India-CMC : 2023-10-13 {.unlisted .unnumbered}

\newpage

# Part I. Within Site Report

```{r define function for site}
plot_site <- function(site){
  df_ftg_long <- df_ftg_long %>% 
    filter(SITE == site)
  
  ggplot(df_ftg_long, aes(x = Variable, fill = Value)) +
    geom_bar(alpha = 0.9, position = "fill") +
    scale_fill_manual(
      values = c("lightgrey", "#F0833A", "#FFCBA4", 
                 "#FEEFCE", "darkseagreen2", "#70B23F"),
      drop = FALSE) + 
    xlab("") + 
    ylab("") +
    facet_grid(M26_TYPE_VISIT~., scales = "free_y", margins = TRUE) + 
    theme_bw() +  
    theme(legend.title = element_blank()) +
    theme(strip.background=element_rect(fill="white")) 
}

```

## Variable list
* Q1. Feel tired (FTGE_AN2).
* Q2. Feel fatigued (FTGE_HI7).
* Q3. Feel weak (FTGE_HI12).
* Q4. Feel listless ("washed out") (FTGE_AN1V).
* Q5. Have trouble starting things because of the tiredness (FTGE_AN3).
* Q6. Have trouble finishing things because of the tiredness (FTGE_AN4).
* Q7. Have no energy (FTGE_AN5).
    + FTGE_AN5 is "Have energy" with answer choices "0, Not at all; 1, A little bit; 2, Somewhat; 3, Quite a bit; 4, Very much". In order to be aligned with the rest questions in a sense of fatigue level, we derived Q7 by flipping the answer choices of FTGE_AN5 and labeled it as "Have no energy". 
* Q8. Unable to do usual activities (FTGE_AN7).
    + FTGE_AN7 is "Able to do usual activities" with answer choices "0, Not at all; 1, A little bit; 2, Somewhat; 3, Quite a bit; 4, Very much". In order to be aligned with the rest questions in a sense of fatigue level, we derived Q8 by flipping the answer choices of FTGE_AN7 and labeled it as "Unable to do usual activities". 
* Q9. Need to sleep during the day (FTGE_AN8).
* Q10. Too tired to eat (FTGE_AN12).
* Q11. Need help doing usual activities (FTGE_AN14).
* Q12. Frustrated by being too tired to do the things want to do (FTGE_AN15).
* Q13. Have to limit social activity because of the tiredness (FTGE_AN16).

  -- Note that NA means variable values are not one of the response options, such as -5, -7, 55, 77, etc. 
    
## Site 1. Pakistan

```{r}
plot_site("Pakistan")

```

## Site 2. Kenya

```{r}
plot_site("Kenya")

```

## Site 3. Ghana

```{r}
plot_site("Ghana")

```

## Site 4. Zambia

```{r}
plot_site("Zambia")

```

## Site 5. India-CMC

```{r}
plot_site("India-CMC")

```

\newpage

# Part II. Between Site Report

```{r define function for question}
plot_q <- function(n){
  ggplot(df_ftg, 
         aes(x = SITE, 
             fill = eval(parse(text=paste0("Q", n))))) +
    geom_bar(alpha = 0.9, position = "fill") +
    scale_fill_manual(
      values = c("lightgrey", "#F0833A", "#FFCBA4", 
                 "#FEEFCE", "darkseagreen2", "#70B23F"), 
      drop = FALSE) + 
    xlab("") + 
    ylab("") +
    facet_grid(M26_TYPE_VISIT~., scales = "free_y", margins = TRUE) + 
    theme_bw() +  
    theme(legend.title = element_blank()) +
    theme(strip.background=element_rect(fill="white"))
}

```

## Q1. Feel tired (FTGE_AN2).

```{r}
plot_q(1)

```

## Q2. Feel fatigued (FTGE_HI7).

```{r}
plot_q(2)

```

## Q3. Feel weak (FTGE_HI12).

```{r}
plot_q(3)

```

## Q4. Feel listless ("washed out") (FTGE_AN1V).

```{r}
plot_q(4)

```

## Q5. Have trouble starting things because of the tiredness (FTGE_AN3).

```{r}
plot_q(5)

```

## Q6. Have trouble finishing things because of the tiredness (FTGE_AN4).

```{r}
plot_q(6)

```

## Q7. Have no energy (FTGE_AN5).

```{r}
plot_q(7)

```

## Q8. Unable to do usual activities (FTGE_AN7).

```{r}
plot_q(8)

```

## Q9. Need to sleep during the day (FTGE_AN8).

```{r}
plot_q(9)

```

## Q10. Too tired to eat (FTGE_AN12).

```{r}
plot_q(10)

```

## Q11. Need help doing usual activities (FTGE_AN14).

```{r}
plot_q(11)

```

## Q12. Frustrated by being too tired to do the things want to do (FTGE_AN15).

```{r}
plot_q(12)

```

## Q13. Have to limit social activity because of the tiredness (FTGE_AN16).

```{r}
plot_q(13)

```
\newpage
# III. Part 3 Fatigue subscale score by site

Fatigue Subscale Scoring is calculated according to FACIT-Fatigue Subscale Scoring Guidelines (Version 4). Score range is 0-52.
Instructions:
1. Record answers in "item response" column. If missing, mark with an X
2. Perform reversals as indicated and sum individual items to obtain a score.
3. Multiply the sum of the item scores by the number of items in the subscale, then divide by the number of items answered.  This produces the subscale score.
4. **The higher the score, the better the QOL.**


```{r}
plot_ftg_score <- df_ftg %>%   
  filter(!is.na(ftg_score))  

plot_ftg_score %>%
  ggplot(aes(x = ftg_score, fill = ..x..)) +
  geom_histogram( alpha=0.9, position="identity", binwidth = 1) +
  scale_x_continuous(breaks=seq(0,52,1))+
  xlab("Fatigue Subscale Score") +
  ylab("Frequency")+
  facet_grid(SITE~., scales = "free_y", margins = FALSE) +
  theme_bw() +
  theme(strip.background=element_rect(fill="white"),
        axis.text.x = element_text(angle = 90, vjust = 1, hjust=1),
        legend.position="bottom",
        legend.title = element_blank(),
        panel.grid.minor = element_blank(),
        axis.text = element_text(size = 8),
        axis.title = element_text(size = 9),
        legend.text = element_text(size = 8)) +
scale_fill_gradient(low='red', high='green')

```

