---
title: "Depression form (MNH25) analysis"
date: "`r Sys.Date()`"
output:
  pdf_document:
    toc: true
    toc_depth: 3
    latex_engine: xelatex
    keep_tex: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE, out.width = "100%", fig.align = "center") 

library(tidyverse)
library(flextable)
library(officer)
library(scales) 
library(patchwork)

load("derived_data/df_depress.rda")

#table format
tb_flextable <- function(data, caption, seq_id, bkm) { 
  tb <- qflextable(data)
  tb <- set_table_properties(
    tb, width = 0.8, layout = "autofit",
    opts_pdf = list(tabcolsep = 3))
  tb <- set_caption(tb,
    caption = as_paragraph(
as_chunk(caption, props = fp_text_default(font.family = "Arial"))
),
    word_stylename = "Table Caption",
    autonum = run_autonum(seq_id = seq_id, bkm = bkm)
  )
  tb <- bold(tb, bold = FALSE, part = "header")
  tb
}
```

### Includes data from synapse last updated: {.unlisted .unnumbered}
### Pakistan : 2023-10-13 {.unlisted .unnumbered}
### Kenya : 2023-10-13 {.unlisted .unnumbered}
### Ghana : 2023-10-13 {.unlisted .unnumbered}
### Zambia : 2023-10-13 {.unlisted .unnumbered}
### India-CMC : 2023-10-13 {.unlisted .unnumbered}

\newpage

## Part I. Depression score distribution by site

Depression score range is 0-30. The higher the score, the higher likelihood of depression. Please refer to the cutoff line for each site.

```{r}
plot_depress_k <- df_depress %>%   
  filter(!is.na(dep_score)) %>% 
  filter(SITE == "Kenya")

plot_depress_p <- df_depress %>%   
  filter(!is.na(dep_score)) %>% 
  filter(SITE == "Pakistan")

plot_depress_g <- df_depress %>%   
  filter(!is.na(dep_score)) %>% 
  filter(SITE == "Ghana")

plot_depress_i <- df_depress %>%   
  filter(!is.na(dep_score)) %>% 
  filter(SITE == "India-CMC")

plot_depress_z <- df_depress %>%   
  filter(!is.na(dep_score)) %>% 
  filter(SITE == "Zambia")

df_vline <- data.frame(
  vline = c(13,11,14,8,10),
  SITE = c("Kenya","Ghana","Pakistan","India-CMC","Zambia"))

p_k <- ggplot(plot_depress_k, aes(x = dep_score, fill = ..x..)) +
  geom_histogram(alpha=0.8, position="identity", binwidth = 1) +
  scale_x_continuous(breaks=seq(0,30,1), limits = c(-1,31))+
  xlab("") +
  ylab("Kenya")+
  theme_bw() +
  theme(strip.background=element_rect(fill="white"),
        axis.text.x = element_blank(),
        legend.position="right",
        legend.title = element_blank(),
        panel.grid.minor = element_blank(),
        axis.text = element_text(size = 8),
        axis.title = element_text(size = 9),
        legend.text = element_text(size = 6),
        legend.key.size = unit(0.236,"cm"),
        plot.margin = unit(c(0,0,0,0), "pt"),
        axis.ticks.x = element_blank()
        ) +
  geom_vline(data=df_vline, aes(xintercept = 13), color = "red",size=0.15) +
  scale_fill_gradientn(colours = c("green", "yellow", "blue3", "darkblue"), 
                       values = c(0, 13/30, (13/30+1)/2, 1))


p_g <- ggplot(plot_depress_g, aes(x = dep_score, fill = ..x..)) +
  geom_histogram(alpha=0.8, position="identity", binwidth = 1) +
  scale_x_continuous(breaks=seq(0,30,1), limits = c(-1,31))+
  xlab("") +
  ylab("Ghana")+
  theme_bw() +
  theme(strip.background=element_rect(fill="white"),
        axis.text.x = element_blank(),
        legend.position="right",
        legend.title = element_blank(),
        panel.grid.minor = element_blank(),
        axis.text = element_text(size = 8),
        axis.title = element_text(size = 9),
        legend.text = element_text(size = 6),
        legend.key.size = unit(0.236,"cm"),
        plot.margin = unit(c(0,0,0,0), "pt"),
                axis.ticks.x = element_blank()
        ) +
  geom_vline(aes(xintercept = 11), color = "red",size=0.15) +
   scale_fill_gradientn(colours = c("green", "yellow", "blue3", "darkblue"), 
                        values = c(0, 11/30, (11/30+1)/2, 1))

p_i <- ggplot(plot_depress_i, aes(x = dep_score, fill = ..x..)) +
  geom_histogram(alpha=0.8, position="identity", binwidth = 1) +
  scale_x_continuous(breaks=seq(0,30,1), limits = c(-1,31))+
  xlab(" ") +
  ylab("India-CMC")+
  theme_bw() +
  theme(strip.background=element_rect(fill="white"),
        axis.text.x = element_blank(),
        legend.position="right",
        legend.title = element_blank(),
        panel.grid.minor = element_blank(),
        axis.text = element_text(size = 8),
        axis.title = element_text(size = 9),
        legend.text = element_text(size = 6),
        legend.key.size = unit(0.236,"cm"),
        plot.margin = unit(c(0,0,0,0), "pt"),
        axis.ticks.x = element_blank()
        ) +
  geom_vline(data=df_vline, aes(xintercept = 8), color = "red",size=0.15) +
 scale_fill_gradientn(colours = c("green", "yellow", "blue3", "darkblue"), 
                      values = c(0, 8/30, (8/30+1)/2, 1))

p_p <- ggplot(plot_depress_p, aes(x = dep_score, fill = ..x..)) +
  geom_histogram(alpha=0.8, position="identity", binwidth = 1) +
  scale_x_continuous(breaks=seq(0,30,1), limits = c(-1,31))+
  xlab("") +
  ylab("Pakistan")+
  theme_bw() +
  theme(strip.background=element_rect(fill="white"),
        axis.text.x = element_blank(),
        legend.position="right",
        legend.title = element_blank(),
        panel.grid.minor = element_blank(),
        axis.text = element_text(size = 8),
        axis.title = element_text(size = 9),
        legend.text = element_text(size = 6),
        legend.key.size = unit(0.236,"cm"),
        plot.margin = unit(c(0,0,0,0), "pt"),
        axis.ticks.x = element_blank()
        ) +
  geom_vline(aes(xintercept = 14), color = "red",size=0.15) +
 scale_fill_gradientn(colours = c("green", "yellow", "blue3", "darkblue"), 
                      values = c(0, 14/30, (14/30+1)/2, 1))

p_z <- ggplot(plot_depress_z, aes(x = dep_score, fill = ..x..)) +
  geom_histogram(alpha=0.8, position="identity", binwidth = 1) +
  scale_x_continuous(breaks=seq(0,30,1), limits = c(-1,31))+
  xlab("Depression Score") +
  ylab("Zambia")+
  theme_bw() +
  theme(strip.background=element_rect(fill="white"),
        axis.text.x = element_text(angle = 0, vjust = 1, hjust=1),
        legend.position="right",
        legend.title = element_blank(),
        panel.grid.minor = element_blank(),
        axis.text = element_text(size = 8),
        axis.title = element_text(size = 9),
        legend.text = element_text(size = 6),
        legend.key.size = unit(0.236,"cm"), 
        plot.margin = unit(c(0,0,0,0), "pt")
        ) +
  geom_vline(data=df_vline, aes(xintercept = 10), color = "red",size=0.15) +
   scale_fill_gradientn(colours = c("green", "yellow", "blue3", "darkblue"), 
                        values = c(0, 10/30, (10/30+1)/2, 1))

wrap_plots(list(p_g,plot_spacer(),p_i,plot_spacer(),p_k,plot_spacer(),p_p,plot_spacer(),p_z), ncol = 1,heights = 50) +
  plot_layout(heights = c(7,-2.7,7,-2.7,7,-2.7,7,-2.7,7),guides = "keep") 


```

\textcolor{red}{|} indicates the cutoff score for depression likelihood in each site. And percent of mom who has higher than cutoff score are shown below.

```{r}
tb_depress <- df_depress %>%
  group_by(SITE) %>%
  summarise(
    "Possible Depression, n (%)" = paste0(
      format(sum(dep_lh == 1, na.rm = TRUE), nsmall = 0, digits = 2),
      " (",
      format(round(sum(dep_lh == 1, na.rm = TRUE)/n()*100, 2), nsmall = 2, digits = 2),
      ")")
  ) %>% 
  ungroup() 

  tb_flextable(tb_depress, "Percent of possibly depressed mom", seq_id = "tb", bkm = "tb1")
```

## PartII. Suicidal intent by site
```{r}
plot_suicidal <- df_depress 

plot_suicidal %>%
  ggplot(aes(x = visit_window, fill=suicidal)) +
    geom_bar(alpha = 0.9, aes(y = (..count..)/sum(..count..)), position = "fill") +
     scale_y_continuous(labels=percent) +
    scale_fill_manual(
      values = c("#c93212", "#00755e" , "grey"),  
      drop = FALSE) + 
    xlab("") + 
    ylab("") +
    facet_grid(~SITE, scales = "free_y", margins = FALSE) + 
    theme_bw() +  
theme(axis.text.x = element_text(angle = 90, vjust = 1, hjust=1),
      strip.background=element_rect(fill="white"),
        legend.position="right",
        legend.title = element_blank(),
        panel.grid.minor = element_blank(),
        axis.text = element_text(size = 9),
        axis.title = element_text(size = 8))
```
