---
title: "Mat_GDM_tables"
author: "Fouzia Farooq"
date: "`r Sys.Date()`"
output:
  html_document:
    df_print: paged
    toc: yes
    toc_depth: 4
  word_document:
    toc: yes
    toc_depth: '4'
  pdf_document:
    toc: yes
    toc_depth: '4'
    df_print: kable
always_allow_html: true
---

&nbsp;
&nbsp;
&nbsp;
&nbsp;


##### **Includes data from synapse last updated:** {.unlisted .unnumbered}
#####  2023-10-06 {.unlisted .unnumbered}


```{css, echo=FALSE}
.table caption {
  color: black;
  font-weight: bold;
}
```


```{r, data setup, include = FALSE}

knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
```

```{r}
library(knitr)
library(tidyverse)
library(reshape2)
library(lubridate)
library(kableExtra)
library(emo)
library(naniar)
library(dplyr)
library(RColorBrewer)
```

```{r}
# AMONG WOMEN WHO HAVE A VISIT 3 (ANC28)
diabetes_df <- read.csv('../data_out/mat_diabetes_fortables.csv', header = TRUE)
df <- diabetes_df # the file that is generated in 'Mat_GDM_analysis.Rmd' -- run that first but make sure to subset on VISIT 3.
```
\newpage

### Gestational Diabetes 
**Definition:** Diabetes first diagnosed during pregnancy (at ≥20 weeks’ gestation), characterized by insulin resistance and high blood sugar. 
<br>
Thresholds for 75g oral glucose tolerance test (OGTT) per the 2010 International Association Of Diabetes And Pregnancy Study Groups (IADPSG) guidelines:
<br>
Fasting Glucose >= 5.1 mmol/L
<br>
1-hr OGTT >= 10.0 mmol/L
<br>
2-hr OGTT >= 8.5 mmol/L

<br>
<br>

**Denominator:** Enrolled women who have a gestational age>=20 wks and have an ANC-28 (VISIT 3) among women without overt diabetes.
<br>
<br>


```{r echo=FALSE}
CONVERT_NA <- FALSE
if(CONVERT_NA ==TRUE){
  
  df <- df %>% #b/c I am passing in the entire dataframe, I don't need to specify the first parameter.
    mutate_all(function(d) {
      if_else(d=="1907-07-07", NA, d)
    })
  
  df <- df %>% #b/c I am passing in the entire dataframe, I don't need to specify the first parameter.
    mutate_all(function(d) {
      if_else(d==-7, NA, d)
    })
  
  df <- df %>% #b/c I am passing in the entire dataframe, I don't need to specify the first parameter.
    mutate_all(function(d) {
      if_else(d==77, NA, d)
    })
  
  # -5 IS MISSING FOR CONTINOUS
  df <- df %>% #b/c I am passing in the entire dataframe, I don't need to specify the first parameter.
    mutate_all(function(d) {
      if_else(d==-5, NA, d)
    })
  
  # 55 IS MISSING FOR CATEGORICAL
  df <- df %>% #b/c I am passing in the entire dataframe, I don't need to specify the first parameter. 
    mutate_all(function(d) {
      if_else(d==55, NA, d) 
    })
  
  # 55:55 IS MISSING FOR TIME
  df <- df %>% #b/c I am passing in the entire dataframe, I don't need to specify the first parameter. 
    mutate_all(function(d) {
      if_else(d=='55:55', NA, d)
    })
}
```

**Table 1a: Data Missingness**
```{r}
test.df <- df %>% filter(SITE=="Ghana") %>% select(MOMID, PREGID, SITE, M08_HBA1C_PRCNT_1) # most of Ghana's data is -5 in the csv raw also.

sum((test.df$M08_HBA1C_PRCNT_1==-5))

diabetes_table <- df %>%
  rowwise() %>%
  group_by(SITE) %>%
  summarise(
    ########## MEASURED
    "Missing MNH08 Enrollment form*, n (%)" = 
      paste0(sum(M08_MAT_VISIT_FORM_COMPLETED_1==0),
             " (",
             format(round(sum(M08_MAT_VISIT_FORM_COMPLETED_1==0)/n()*100, 2),nsmall=2, digits=3), # this ALREADY INCLUDES WINDOW HAS PASSED B/C I HAVE SUBSUTTED TO ANC28 WINDOW PASS==1.  COULD ALSO HAVE DONE USING OVERDUE==1.  AND THEN I WOULD DIVIDE BY everyone who is passed the window. 
             ")"),
    # HBA1C IS MEASURED AT ENROLLMENT
    "Missing HbA1c: M08_HBA1C_PRCNT_1**, n (%)" =
      paste0(sum(is.na(M08_HBA1C_PRCNT_1), (M08_HBA1C_PRCNT_1==-5), (M08_HBA1C_PRCNT_1==-7)), # & COMPLETED FORM DIVIDED BY EVERYONE WITH FORM COMPLETED. 
             " (",
             format(round(sum(is.na(M08_HBA1C_PRCNT_1), 
                              (M08_HBA1C_PRCNT_1==-5), 
                              (M08_HBA1C_PRCNT_1==-7))/(sum(M08_MAT_VISIT_FORM_COMPLETED_1==1))*100, 2),nsmall=2, digits=3), # this is total missing the variable out of those who have completed the form.
             ")"),
    
    "Missing MNH08 form at ANC28***, n (%)" = 
      paste0(sum(M08_MAT_VISIT_FORM_COMPLETED_3==0),
             " (",
             format(round(sum(M08_MAT_VISIT_FORM_COMPLETED_3==0)/(sum(ANC28_PASS==3))*100, 2),nsmall=2, digits=3), # this is missing the ANC28 form out of everyone who has passed ANC28
             ")"),
    
    "Missing ANC28 Pretest Fasting Glucose: M08_BGLUC_PRETEST_MMOLL_LBORRES_3, n (%)" =
      paste0(sum(is.na(M08_BGLUC_PRETEST_MMOLL_LBORRES_3), 
                 (M08_BGLUC_PRETEST_MMOLL_LBORRES_3==-5), 
                 (M08_BGLUC_PRETEST_MMOLL_LBORRES_3==-7)),
             " (",
             format(round(sum(is.na(M08_BGLUC_PRETEST_MMOLL_LBORRES_3), 
                              (M08_BGLUC_PRETEST_MMOLL_LBORRES_3==-5),
                              (M08_BGLUC_PRETEST_MMOLL_LBORRES_3==-7))/sum(M08_MAT_VISIT_FORM_COMPLETED_3==1)*100, 2),nsmall=2, digits=3),
             ")"),
    
    # when fasting OGTT is high, then 1-hr (_2) or 2-hr (-3) should be also high 
    # 1-hr (_2) test:
    "Missing ANC28 1-hr OGTT: M08_BGLUC_ORAL_1HR_MMOLL_LBORRES_3, n (%)" =
      paste0(sum(is.na(M08_BGLUC_ORAL_1HR_MMOLL_LBORRES_3), 
                 (M08_BGLUC_ORAL_1HR_MMOLL_LBORRES_3==-7), 
                 (M08_BGLUC_ORAL_1HR_MMOLL_LBORRES_3==-5)),
             " (",
             format(round(sum(is.na(M08_BGLUC_ORAL_1HR_MMOLL_LBORRES_3), 
                              (M08_BGLUC_ORAL_1HR_MMOLL_LBORRES_3==-7),
                              (M08_BGLUC_ORAL_1HR_MMOLL_LBORRES_3==-5))/sum(M08_MAT_VISIT_FORM_COMPLETED_3==1)*100, 2),nsmall=2, digits=3),
             ")"),
    
    # 2-hr (_3) test:
    " Missing ANC28 2-hr OGTT: M08_BGLUC_ORAL_2HR_MMOLL_LBORRES_3, n (%)" =
      paste0(sum(is.na(M08_BGLUC_ORAL_2HR_MMOLL_LBORRES_3), 
                       (M08_BGLUC_ORAL_2HR_MMOLL_LBORRES_3==-5),
                       (M08_BGLUC_ORAL_2HR_MMOLL_LBORRES_3==-7)),
             " (",
             format(round(sum(is.na(M08_BGLUC_ORAL_2HR_MMOLL_LBORRES_3),
                              (M08_BGLUC_ORAL_2HR_MMOLL_LBORRES_3==-5),
                              (M08_BGLUC_ORAL_2HR_MMOLL_LBORRES_3==-7))/sum(M08_MAT_VISIT_FORM_COMPLETED_3==1)*100, 2),nsmall=2, digits=3),
             ")")) %>%

  t() %>% as.data.frame() %>% 
  `colnames<-`(c(.[1,])) %>% 
  slice(-1)
```


```{r}
diabetes_table  %>% 
  `rownames<-` (c(
    "Missing MNH08 Enrollment form, n (%)",
    "Missing Enrollment HbA1c: M08_HBA1C_PRCNT, n (%)",
    "Missing MNH08 form at ANC28, n (%)",
    "Missing ANC28 Pretest Fasting Glucose: M08_BGLUC_PRETEST_MMOLL_LBORRES, n (%)",
    "Missing ANC28 1-hr OGTT: M08_BGLUC_ORAL_1HR_MMOLL_LBORRES, n (%)",
    "Missing ANC28 2-hr OGTT: M08_BGLUC_ORAL_2HR_MMOLL_LBORRES, n (%)")) %>% 
    
  mutate_all(funs(str_replace(., "NaN", "0"))) %>% 
  kbl(caption = "", booktabs = TRUE) %>%
  kable_paper(bootstrap_options = "striped", 
              full_width = T, html_font = "Cambria", position = "left",
              latex_options = c("repeat_header", "HOLD_position")) %>% 
  kable_styling(font_size = 14) %>%
  row_spec(0, extra_css = "border-bottom: 0px white;") 
```
*Among those who have a GA>=20 (passed their enrollment)
**Among those who have a GA>=20 (passed their enrollment) and has completed MNH08 enrollment form
***Among those who have a GA>30 (passed their ANC28 window)
****Among those who have a GA>30 (passed their ANC28 window) and have completed MNH08 ANC-28

Among those who have a GA>=20 (passed their enrollment window)

\newpage

**Table 1b. Prevalence of Gestational Diabetes (any method)**
```{r}
diabetes_table <- df %>%
  rowwise() %>%
  group_by(SITE) %>%
  summarise(
    # GDM CATEGORIES:
    "GDM = Yes " = 
      paste0(sum(GEST_DIAB_MEAS == 1, na.rm = TRUE),
             " (",
             format(round(sum(GEST_DIAB_MEAS == 1, na.rm = TRUE)/n()*100,2), nsmall=2, digits=3), # this is among those who have passed the ANC28 window. I could do this as those who have completed the form. 
             ")"),
    
    "GDM = No " = 
      paste0(sum(GEST_DIAB_MEAS == 0, na.rm = TRUE),
             " (",
             format(round(sum(GEST_DIAB_MEAS == 0, na.rm = TRUE)/n()*100,2), nsmall=2, digits=3),
             ")"),
    
        "GDM = Missing " = 
      paste0(sum(is.na(GEST_DIAB_MEAS)),
             " (",
             format(round(sum(is.na(GEST_DIAB_MEAS))/n()*100,2), nsmall=2, digits=3),
             ")")) %>%

  t() %>% as.data.frame() %>% 
  `colnames<-`(c(.[1,])) %>% 
  slice(-1)
```

```{r}
diabetes_table  %>% 
  `rownames<-` (c( 
    "Yes, n (%)", # Gestational Diabetes (from GEST_DIAB_MEAS)
    "No, n (%)", # Gestational Diabetes (from GEST_DIAB_MEAS)
    "Missing (Fasting, 1-hr OGTT and 2-hr OGTT), n (%)")) %>%
    
     mutate_all(funs(str_replace(., "NaN", "0"))) %>% 
  kbl(caption = "", booktabs = TRUE) %>%
  kable_paper(bootstrap_options = "striped", 
              full_width = T, html_font = "Cambria", position = "left",
              latex_options = c("repeat_header", "HOLD_position")) %>% 
  kable_styling(font_size = 14) %>%
  row_spec(0, extra_css = "border-bottom: 0px white;") %>%
  
  pack_rows("Gestational Diabetes (Any method), n (%)", 1, 3, label_row_css = "color: steelblue;")
```

**Table 1c. Prevalence of gestational diabetes by each method**
```{r}

diabetes_table <- df %>%
  rowwise() %>%
  group_by(SITE) %>%
  summarise(
    # Overt Diabetes: M08_HBA1C_PRCNT_1
     "Overt Diabetes = Yes " =
      paste0(sum(OVERT_DIA == 1, na.rm = TRUE),
             " (",
             format(round(sum(OVERT_DIA == 1, na.rm = TRUE)/n()*100,2), nsmall=2, digits=3),
             ")"),

         "Overt Diabetes = No " =
      paste0(sum(OVERT_DIA == 0, na.rm = TRUE),
             " (",
             format(round(sum(OVERT_DIA == 0, na.rm = TRUE)/n()*100,2), nsmall=2, digits=3),
             ")"),

         "Overt Diabetes = Missing " =
      paste0(sum(is.na(OVERT_DIA)),
             " (",
             format(round(sum(is.na(OVERT_DIA))/n()*100,2), nsmall=2, digits=3),
             ")"),

    # OGTT_PRE
        "Fasting Glucose = Yes " =
      paste0(sum(OGTT_PRE == 1, na.rm = TRUE),
             " (",
             format(round(sum(OGTT_PRE == 1, na.rm = TRUE)/n()*100,2), nsmall=2, digits=3),
             ")"),

            "Fasting Glucose = No " =
      paste0(sum(OGTT_PRE == 0, na.rm = TRUE),
             " (",
             format(round(sum(OGTT_PRE == 0, na.rm = TRUE)/n()*100,2), nsmall=2, digits=3),
             ")"),

               "Fasting Glucose = Missing " =
      paste0(sum(is.na(OGTT_PRE)),
             " (",
             format(round(sum(is.na(OGTT_PRE))/n()*100,2), nsmall=2, digits=3),
             ")"),


    # OGTT 1-hr
        "OGTT 1-hr = Yes " =
      paste0(sum(OGTT_1hr == 1, na.rm = TRUE),
             " (",
             format(round(sum(OGTT_1hr == 1, na.rm = TRUE)/n()*100,2), nsmall=2, digits=3),
             ")"),

            "OGTT 1-hr = No " =
      paste0(sum(OGTT_1hr == 0, na.rm = TRUE),
             " (",
             format(round(sum(OGTT_1hr == 0, na.rm = TRUE)/n()*100,2), nsmall=2, digits=3),
             ")"),

               "OGTT 1-hr = Missing " =
      paste0(sum(is.na(OGTT_1hr)),
             " (",
             format(round(sum(is.na(OGTT_1hr))/n()*100,2), nsmall=2, digits=3),
             ")"),

        # OGTT 2-hr
        "OGTT 2-hr = Yes " =
      paste0(sum(OGTT_2hr == 1, na.rm = TRUE),
             " (",
             format(round(sum(OGTT_2hr == 1, na.rm = TRUE)/n()*100,2), nsmall=2, digits=3),
             ")"),

            "OGTT 2-hr = No " =
      paste0(sum(OGTT_2hr == 0, na.rm = TRUE),
             " (",
             format(round(sum(OGTT_2hr == 0, na.rm = TRUE)/n()*100,2), nsmall=2, digits=3),
             ")"),

               "OGTT 2-hr = Missing " =
      paste0(sum(is.na(OGTT_2hr)),
             " (",
             format(round(sum(is.na(OGTT_2hr))/n()*100,2), nsmall=2, digits=3),
             ")")) %>%

  t() %>% as.data.frame() %>% 
  `colnames<-`(c(.[1,])) %>% 
  slice(-1)
  
```

```{r}
diabetes_table  %>% 
  `rownames<-` (c(
    "HbA1c Yes, n (%)", # Hba1c / Overt Diabetes
    "HbA1c No, n (%)",
    "Missing (HbA1c)*, n(%)",
    "Fasting Glucose Yes, n (%)", # Fasting Glucose
    "Fasting Glucose No, n (%)",
    "Missing (Fasting), n(%)",
    "OGTT 1-hr Yes, n (%)", # OGTT 1-hr
    "OGTT 1-hr No, n (%)",
    "Missing (OGTT 1-hr), n(%)",
    "OGTT 2-hr Yes, n (%)",# OGTT 2-hr
    "OGTT 2-hr No, n (%)",
    "Missing (OGTT 2-hr), n(%)")) %>%
  
  
  mutate_all(funs(str_replace(., "NaN", "0"))) %>% 
  kbl(caption = "", booktabs = TRUE) %>%
  kable_paper(bootstrap_options = "striped", 
              full_width = T, html_font = "Cambria", position = "left",
              latex_options = c("repeat_header", "HOLD_position")) %>% 
  kable_styling(font_size = 14) %>%
  row_spec(0, extra_css = "border-bottom: 0px white;") %>%
  
  pack_rows("HbA1c [HBA1C_PRCNT] (>=6.5%), n (%)", 1, 3, label_row_css = "color: steelblue;") %>%
  pack_rows("Fasting Glucose [BGLUC_PRETEST_MMOLL_LBORRES] (>=5.1 mmol/L), n (%)", 4, 6, label_row_css = "color: steelblue;") %>%
  pack_rows("OGTT 1-hr [BGLUC_ORAL_1HR_MMOLL_LBORRES] (>=10.0 mmol/L), n (%)", 7, 9, label_row_css = "color: steelblue;") %>%
  pack_rows("OGTT 2-hr [BGLUC_ORAL_2HR_MMOLL_LBORRES] (>=8.5 mmol/L), n (%)", 10, 12, label_row_css = "color: steelblue;")
  
```
**Among those who have a GA>=20 (passed their enrollment)
\newpage

#### Figure 1a. Histogram of HbA1c % across sites
```{r fig1}

hba1c_nomissing <- df %>% filter(!is.na(M08_HBA1C_PRCNT_1)) %>% filter(M08_HBA1C_PRCNT_1!=-5 & M08_HBA1C_PRCNT_1!=-7)

ggplot(data=hba1c_nomissing,
       aes(x=M08_HBA1C_PRCNT_1)) +
  geom_histogram() + # binwidth = 10 +
  facet_grid(vars(SITE), scales = "free") +
  scale_x_continuous(breaks = seq(0,100,2)) + # RANGE FOR OGTT HERE ON X-AXIS IS 0-30 .
  ggtitle("Percent HbA1c distribution , by site") +
  ylab("Count") +
  xlab("HbA1c (%)") +
  theme_bw() +
  theme(strip.background=element_rect(fill="white")) + #color
  theme(axis.text.x = element_text(vjust = 1, hjust=1), # angle = 60,
        legend.position="bottom",
        legend.title = element_blank(),
        panel.grid.minor = element_blank()) +
    #geom_vline(mapping=aes(xintercept=0), linetype ="dashed", color = "red") + # ADDS VERTICAL DASHED LINE AT MIN THRESHOLD
  geom_vline(mapping=aes(xintercept=6.5), linetype ="dashed", color = "red")  # ADDS VERTICAL DASHED LINE AT MAX THRESHOLD

```

#### Figure 2a. Histogram of Fasting Glucose across sites
```{r fig2a}

fasting_gluc_nomissing <- df %>% 
  filter(!is.na(M08_BGLUC_PRETEST_MMOLL_LBORRES_3)) %>% 
  filter(M08_BGLUC_PRETEST_MMOLL_LBORRES_3!=-5 & M08_BGLUC_PRETEST_MMOLL_LBORRES_3!=-7)

ggplot(data=fasting_gluc_nomissing,
       aes(x=M08_BGLUC_PRETEST_MMOLL_LBORRES_3)) +
  geom_histogram() + # binwidth = 10 +
  facet_grid(vars(SITE), scales = "free") +
  scale_x_continuous(breaks = seq(0,10,2)) + # .
  ggtitle("Fasting glucose distribution , by site") +
  ylab("Count") +
  xlab("Fasting glucose (mmol/L)") +
  theme_bw() +
  theme(strip.background=element_rect(fill="white")) + #color
  theme(axis.text.x = element_text(vjust = 1, hjust=1), # angle = 60,
        legend.position="bottom",
        legend.title = element_blank(),
        panel.grid.minor = element_blank()) +
    geom_vline(mapping=aes(xintercept=0), linetype ="dashed", color = "red") + # ADDS VERTICAL DASHED LINE AT MIN THRESHOLD at 0
  geom_vline(mapping=aes(xintercept=5.1), linetype ="dashed", color = "red")  # ADDS VERTICAL DASHED LINE AT cutoff of 5.1 for diagnosis of GDM

```

#### Figure 2b. Histogram of OGTT 1hr across sites
```{r fig2b}

OGTT1hr_nomissing <- df %>% filter(!is.na(M08_BGLUC_ORAL_1HR_MMOLL_LBORRES_3)) %>%
  filter(M08_BGLUC_ORAL_1HR_MMOLL_LBORRES_3!=-5 & M08_BGLUC_ORAL_1HR_MMOLL_LBORRES_3!=-7)

ggplot(data=OGTT1hr_nomissing,
       aes(x=M08_BGLUC_ORAL_1HR_MMOLL_LBORRES_3)) +
  geom_histogram() + # binwidth = 10 +
  facet_grid(vars(SITE), scales = "free") +
  scale_x_continuous(breaks = seq(0,30,2)) + # RANGE FOR OGTT HERE ON X-AXIS IS 0-30 .
  ggtitle("1-hr OGTT distribution , by site") +
  ylab("Count") +
  xlab("1-hr OGTT (mmol/L)") +
  theme_bw() +
  theme(strip.background=element_rect(fill="white")) + #color
  theme(axis.text.x = element_text(vjust = 1, hjust=1), # angle = 60,
        legend.position="bottom",
        legend.title = element_blank(),
        panel.grid.minor = element_blank()) +
    geom_vline(mapping=aes(xintercept=0), linetype ="dashed", color = "red") + # ADDS VERTICAL DASHED LINE AT MIN THRESHOLD at 0
  geom_vline(mapping=aes(xintercept=11.1), linetype ="dashed", color = "red")  # ADDS VERTICAL DASHED LINE AT MAX THRESHOLD of 11.1

```

#### Figure 2c. Histogram of OGTT 2-hr across sites
```{r fig2c}

OGTT2hr_nomissing <- df %>% filter(!is.na(M08_BGLUC_ORAL_2HR_MMOLL_LBORRES_3)) %>% 
  filter(M08_BGLUC_ORAL_2HR_MMOLL_LBORRES_3!=-5 & M08_BGLUC_ORAL_2HR_MMOLL_LBORRES_3!=-7)

ggplot(data=OGTT2hr_nomissing,
       aes(x=M08_BGLUC_ORAL_2HR_MMOLL_LBORRES_3)) +
  geom_histogram() + #binwidth = 100
  facet_grid(vars(SITE), scales = "free") +
  scale_x_continuous(breaks = seq(0,30,2)) + # RANGE FOR OGTT HERE ON X-AXIS IS 0-30
  ggtitle("2-hr OGTT distribution , by Site") +
  ylab("Count") +
  xlab("2-hr OGTT (mmol/L)") +
  theme_bw() +
  theme(strip.background=element_rect(fill="white")) + #color
  theme(axis.text.x = element_text(vjust = 1, hjust=1), # angle = 60,
        legend.position="bottom",
        legend.title = element_blank(),
        panel.grid.minor = element_blank()) +
    geom_vline(mapping=aes(xintercept=0), linetype ="dashed", color = "red") + # ADDS VERTICAL DASHED LINE AT MIN THRESHOLD
  geom_vline(mapping=aes(xintercept=8.5), linetype ="dashed", color = "red")  # ADDS VERTICAL DASHED LINE AT upper cutoff

```

<!-- \newpage -->
<!-- Table 2: Gestational Diabetes Diagnosed -->
<!-- ```{r} -->
<!-- # diabetes_df <- diabetes_df %>% -->
<!-- #   mutate(GEST_DIAB_DIAG = case_when((M04_DIABETES_EVER_MHOCCUR_3==0 | M04_DIABETES_EVER_MHOCCUR_4==0 | M04_DIABETES_EVER_MHOCCUR_5==0) & -->
<!-- #                                       ((M09_GEST_DIAB_MHOCCUR_6==1 | # WAS MOTHER DIAGNOSED WITH GDM -->
<!-- #                                       (M09_INDUCED_PROCCUR_6==1 & M09_INDUCED_PRINDC_6==8)) | -->
<!-- #                                       (M19_PRIMARY_MHTERM_13==4 & M19_LD_COMPL_MHTERM_3_13)) ~ 1, -->
<!-- #                                     TRUE ~ as.numeric(0))) -->


<!-- diabetes_table <- df %>% -->
<!--   rowwise() %>% -->
<!--   group_by(SITE) %>% -->
<!--   summarise( -->
<!--     ########## DIAGNOSED -->
<!--     # -->
<!--     "ANC28 - Diagnosed with Diabetes in the past?: M04_DIABETES_EVER_MHOCCUR_3, n (%)" = -->
<!--       paste0(sum(is.na(M04_DIABETES_EVER_MHOCCUR_3)), -->
<!--              " (", -->
<!--              format(round(sum(is.na(M04_DIABETES_EVER_MHOCCUR_3))/n()*100, 2),nsmall=2, digits=3), -->
<!--              ")"), -->

<!--     "ANC32 - Diagnosed with Diabetes in the past?: M04_DIABETES_EVER_MHOCCUR_4, n (%)" = -->
<!--       paste0(sum(is.na(M04_DIABETES_EVER_MHOCCUR_4)), -->
<!--              " (", -->
<!--              format(round(sum(is.na(M04_DIABETES_EVER_MHOCCUR_4))/n()*100, 2),nsmall=2, digits=3), -->
<!--              ")"), -->

<!--     "ANC36 - Diagnosed with Diabetes in the past?: M04_DIABETES_EVER_MHOCCUR_5, n (%)" = -->
<!--       paste0(sum(is.na(M04_DIABETES_EVER_MHOCCUR_5)), -->
<!--              " (", -->
<!--              format(round(sum(is.na(M04_DIABETES_EVER_MHOCCUR_5))/n()*100, 2),nsmall=2, digits=3), -->
<!--              ")"), -->

<!--     "L&D Induced: M09_INDUCED_PROCCUR_6, n (%)" = -->
<!--       paste0(sum(is.na(M09_INDUCED_PROCCUR_6)), -->
<!--              " (", -->
<!--              format(round(sum(is.na(M09_INDUCED_PROCCUR_6))/n()*100, 2),nsmall=2, digits=3), -->
<!--              ")"), -->


<!--     "L&D Induced: M09_INDUCED_PRINDC_6, n (%)" = -->
<!--       paste0(sum(is.na(M09_INDUCED_PRINDC_6)), -->
<!--              " (", -->
<!--              format(round(sum(is.na(M09_INDUCED_PRINDC_6))/n()*100, 2),nsmall=2, digits=3), -->
<!--              ")"), -->


<!--     "Hospitalization: M19_PRIMARY_MHTERM_13, n (%)" = -->
<!--       paste0(sum(is.na(M19_PRIMARY_MHTERM_13)), -->
<!--              " (", -->
<!--              format(round(sum(is.na(M19_PRIMARY_MHTERM_13))/n()*100, 2),nsmall=2, digits=3), -->
<!--              ")"), -->

<!--     "Hospitalization: M19_LD_COMPL_MHTERM_3_13, n (%)" = -->
<!--       paste0(sum(is.na(M19_LD_COMPL_MHTERM_3_13)), -->
<!--              " (", -->
<!--              format(round(sum(is.na(M19_LD_COMPL_MHTERM_3_13))/n()*100, 2),nsmall=2, digits=3), -->
<!--              ")"))%>% -->

<!--   t() %>% as.data.frame() %>% -->
<!--   `colnames<-`(c(.[1,])) %>% -->
<!--   slice(-1) -->

<!-- ``` -->

<!-- ```{r} -->
<!-- diabetes_table  %>% -->
<!--   `rownames<-` (c( -->
<!--     "ANC28 - Diagnosed with Diabetes in the past?: M04_DIABETES_EVER_MHOCCUR_3, n (%)", -->
<!--     "ANC32 - Diagnosed with Diabetes in the past?: M04_DIABETES_EVER_MHOCCUR_4, n (%)", -->
<!--     "ANC36 - Diagnosed with Diabetes in the past?: M04_DIABETES_EVER_MHOCCUR_5, n (%)", -->
<!--     "L&D Induced: M09_INDUCED_PROCCUR_6, n (%)", -->
<!--     "L&D Induced: M09_INDUCED_PRINDC_6, n (%)", -->
<!--     "Hospitalization: M19_PRIMARY_MHTERM_13, n (%)", -->
<!--     "Hospitalization: M19_LD_COMPL_MHTERM_3_13, n (%)")) %>% -->


<!--   mutate_all(funs(str_replace(., "NaN", "0"))) %>% -->
<!--   kbl(caption = "", booktabs = TRUE) %>% -->
<!--   kable_paper(bootstrap_options = "striped", -->
<!--               full_width = T, html_font = "Cambria", position = "left", -->
<!--               latex_options = c("repeat_header", "HOLD_position")) %>% -->
<!--   kable_styling(font_size = 14) %>% -->
<!--   row_spec(0, extra_css = "border-bottom: 0px white;") # -->

<!--  #"Missing M08_CBC_HB_LBORRES_1 = NA, n (%)",#%>% -->
<!--  # pack_rows("PRISMA measured birthweight (categorical), n (%)", 5, 8, label_row_css = "color: steelblue;") %>% -->
<!--   # pack_rows("Any method measured birthweight (categorical), n (%)", 9, 12, label_row_css = "color: steelblue;") -->
<!-- ``` -->

