---
title: "Mat_GDM_analysis"
author: "Fouzia Farooq"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, warning=FALSE}
library(readxl)
library(dplyr)
library(ggplot2)
library(knitr)
library(stringr)
# library(ThemePark)
library(purrr)
library(lubridate)
library(readr)
library(tidyr)
library(haven)
library(tableone)
library(kableExtra)

```

OVERT diabetes = check if a women at enrollment has been diagnosed using hba1c.
GDM: Among women who have an ANC28 and have a GA_AT_VISI>20. 
WOMEN WHO WERE ENROLLED >18 WEEKS WILL NOT HAVE AN ANC20 VISIT FORM BUT THEY SHOULD HAVE ANC28

```{r}
# merged_df <- readRDS('../data_out/merged_df.RDS')
diabetes_df <- read.csv('../data_out/mat_diabetes_vars.csv', header = TRUE)
```

# Convert "1907-07-07" to NA:
# CATEGORICAL: 
# ---- 77, Not applicable 
# ---- 55, Missing 
# ---- 66, Refused to answer
# ---- 99, Don't know

# CONTINUOUS:
# ---- -7, Not applicable 
# ---- -5, Missing 
# ---- -6, Refused to answer
# ---- -9, Don't know
# DATE: 
# ---- 07-07-1907, Not applicable 
# ---- 05-05-1905, Missing 
# ---- 06-06-1906, Refused to answer
# ---- 09-09-1909, Don't know

# TIME: 
# ---- 77:77, Not applicable 
# ---- 55:55, Missing 
# ---- 66:66, Refused to answer
# ---- 99:99, Don't know
```{r echo=FALSE}
CONVERT_NA <- FALSE
if(CONVERT_NA ==TRUE){
  
  diabetes_df <- diabetes_df %>% #b/c I am passing in the entire dataframe, I don't need to specify the first parameter.
    mutate_all(function(d) {
      if_else(d=="1907-07-07", NA, d)
    })
  
  diabetes_df <- diabetes_df %>% #b/c I am passing in the entire dataframe, I don't need to specify the first parameter.
    mutate_all(function(d) {
      if_else(d==-7, NA, d)
    })
  
  diabetes_df <- diabetes_df %>% #b/c I am passing in the entire dataframe, I don't need to specify the first parameter.
    mutate_all(function(d) {
      if_else(d==77, NA, d)
    })
  
  # -5 IS MISSING FOR CONTINOUS
  diabetes_df <- diabetes_df %>% #b/c I am passing in the entire dataframe, I don't need to specify the first parameter.
    mutate_all(function(d) {
      if_else(d==-5, NA, d)
    })
  
  # 55 IS MISSING FOR CATEGORICAL
  diabetes_df <- diabetes_df %>% #b/c I am passing in the entire dataframe, I don't need to specify the first parameter. 
    mutate_all(function(d) {
      if_else(d==55, NA, d) 
    })
  
  # 55:55 IS MISSING FOR TIME
  diabetes_df <- diabetes_df %>% #b/c I am passing in the entire dataframe, I don't need to specify the first parameter. 
    mutate_all(function(d) {
      if_else(d=='55:55', NA, d)
    })
  
}
```

```{r}
window_subset_df <- merged_df %>% 
  select(MOMID, PREGID, SITE, DELIVERED_FF, BOE_GA_WKS, BOE_GA_DAYS, EST_CONCEP_DATE,
         EDD_BOE, GA_ENROLL_WKS, GA_ENROLL_DAYS, DOB, DOB_DATEONLY, 
         
         starts_with(c("M04_MAT_VISIT_FORM_", "M04_MAT_VISIT_wPERSON_",
                     "M08_MAT_VISIT_FORM_", "M08_MAT_VISIT_wPERSON_")),
         
         ENROLL_ONTIME, ENROLL_LATE, 
         ANC20_ONTIME, ANC20_LATE,
         ANC28_ONTIME, ANC28_LATE,
         ANC32_ONTIME, ANC28_LATE,
         ANC36_ONTIME, ANC36_LATE,
         
         M04_ENROLL_OVERDUE, M04_ANC20_OVERDUE, M04_ANC28_OVERDUE,
         M04_ANC32_OVERDUE, M04_ANC36_OVERDUE,
         
         M08_ENROLL_OVERDUE, M08_ANC20_OVERDUE, M08_ANC28_OVERDUE,
         M08_ANC32_OVERDUE, M08_ANC36_OVERDUE,
         
         ENROLL_PASS, ANC20_PASS, ANC28_PASS, ANC32_PASS, ANC36_PASS,
         
         ENROLL_PASS_LATE, ANC20_PASS_LATE, ANC28_PASS_LATE, ANC32_PASS_LATE, ANC36_PASS_LATE,
         
         # GA AT VISIT:
         M04_GA_AT_VISIT_1, M04_GA_AT_VISIT_2, M04_GA_AT_VISIT_3, M04_GA_AT_VISIT_4, M04_GA_AT_VISIT_5,
         M08_GA_AT_VISIT_1,  M08_GA_AT_VISIT_2,  M08_GA_AT_VISIT_3,  M08_GA_AT_VISIT_4,  M08_GA_AT_VISIT_5,
         GA_AT_DELIV_6)# JUST NEED ONE B/C M08 IS OPTIONAL AT DELIVERY)

temp.df <- merged_df %>% filter(SITE=="Zambia") %>% select(MOMID, M08_LBSTDAT_3, M08_MAT_VISIT_MNH08_3,  M08_MAT_VISIT_FORM_COMPLETED_3, M08_MAT_VISIT_wPERSON_COMPLETED_3) # 
```

# SET TO WOMEN WHO HAVE VISIT 3
```{r}
diabetes_df2 <- left_join(diabetes_df, window_subset_df, 
                         by = c("MOMID", "PREGID", "SITE"))

# diabetes_df2 <- diabetes_df  %>% filter(!is.na(M08_LBSTDAT_3)) #THOSE WHO HAVE A VISIT_3 FORM 
```

# WOMEN WHO HAVE A GA >=20 WEEKS
```{r}
diabetes_df3 <- diabetes_df2 %>%
  filter(floor(M08_GA_AT_VISIT_3/7) >=20) %>% 
  filter(ANC28_PASS==1) # Ask Emily - if she wants this or not. 


temp.df2 <- merged_df %>% filter(SITE=="Zambia") %>%
  select(MOMID, SITE, M08_GA_AT_VISIT_3, M08_LBSTDAT_3, M08_BGLUC_ORAL_1HR_MMOLL_LBORRES_3, 
         ANC28_PASS, M08_BGLUC_ORAL_1HR_MMOLL_LBORRES_4, ANC32_PASS,
         EST_CONCEP_DATE, GA_ENROLL_DAYS, M01_US_GA_WKS_AGE_FTS1_1,  GA_US_DAYS_FTS1_1, LMP_GA_DAYS) 
# IF mnh08 overdue ==1, missing the from (for missing variable frequency).  Denominator - everyone who has passed the window. 
```

-5 = missing
-7 = missing
If i am using ANC28_PASS variable (has the ANC28 window passed; if yes = she should have a form), i need to use M08_OVERDUE variable with it to see if she is overdue for the form that she should have or not. (if OVERDUE==1, then that means she's missing the form and the variable will be missing also). Otherwise, I can also just use MAT_VISIT_FORM_COMPLETED variable alone. 

Use: ANC28_PASS==1 and M08_OVERDUE together 
M08_OVERDUE - will show that MNH08 form is missing.They get a =1 only if they are overdue for their visit, so if 0 or NA, she is not overdue. 
otherwise: 
M08_MAT_VISIT_FORM_COMPLETED is missing = 0, then form is missing.

if OVERDUE is 0 or NA and she is still missing _VISIT_FORM, that's not good. 

OVERDUE variables tell us do they have the form or not (when they should have the form)


for HTN here's what I should do: 
If_else GA at enroll >18 or 19 use enrollment visit form only
If GA <=17 weeks, she should have an ANC20 form. use ANC20 visit.

# GESTATIONAL DIABETES - SECONDARY OUTCOME: GEST_DIAB***

Look at: 
- MNH04 ANC28, 32, 36
- MNH06 ANC 28
- MNH08 <20, 28
- MNH09 L&D/IPC: M09_GEST_DIAB_MHOCCUR_6
- MNH19 Hospitalization visit

```{r echo=FALSE}
##################################################################################
#TODO 
# NOTES: 
#TODO HBa1c needs to be checked for Kenya - All are done at enrollment they say
# 1. NEED TO ADD ADDITIONAL CONDITIONS FOR DIAGNOSED # 
# 2. ALL OF MEASURED variables are NA - FASTING OGTT, HbA1c# 

##################################################################################

############ 
# MEASURED # 
############

diabetes_df3 <- diabetes_df3 %>% 
  #dplyr::filter(SITE=="Pakistan") %>%
  mutate(GEST_DIAB_MEAS = case_when((((is.na(M08_HBA1C_PRCNT_1) | M08_HBA1C_PRCNT_1<6.5) & 
                                        ((M08_BGLUC_PRETEST_MMOLL_LBORRES_3>=5.1 | # confirm pre test (fasting) OGTT is high at ANC28
                                           # when fasting OGTT is high, then 1-hr or 2-hr should be also high at ANC28
                                           M08_BGLUC_ORAL_1HR_MMOLL_LBORRES_3>=10.0) |  # 1-hr at ANC28
                                        M08_BGLUC_ORAL_2HR_MMOLL_LBORRES_3 >=8.5))) ~ 1,
                                    
                                    ((is.na(M08_BGLUC_PRETEST_MMOLL_LBORRES_3) |
                                       M08_BGLUC_PRETEST_MMOLL_LBORRES_3==-5 |
                                       M08_BGLUC_PRETEST_MMOLL_LBORRES_3==-7)  & 
                                      
                                      (is.na(M08_BGLUC_ORAL_1HR_MMOLL_LBORRES_3) | 
                                         M08_BGLUC_ORAL_1HR_MMOLL_LBORRES_3==-5 |
                                         M08_BGLUC_ORAL_1HR_MMOLL_LBORRES_3==-7) &
                                      
                                      (is.na(M08_BGLUC_ORAL_2HR_MMOLL_LBORRES_3) | 
                                         M08_BGLUC_ORAL_2HR_MMOLL_LBORRES_3==-5 | 
                                         M08_BGLUC_ORAL_2HR_MMOLL_LBORRES_3==-7)) ~ as.numeric(NA),
                                    TRUE ~ as.numeric(0))) 

table(GEST_DIAB_MEAS = diabetes_df3$GEST_DIAB_MEAS, SITE = diabetes_df3$SITE, useNA = "always")
round(prop.table(table(GEST_DIAB_MEAS = diabetes_df3$GEST_DIAB_MEAS, SITE = diabetes_df3$SITE, useNA = "always"), margin=2)*100,2)

table(diabetes_df3$M08_MAT_VISIT_FORM_COMPLETED_1, useNA = "always")
temp.df <- diabetes_df3 %>% filter(SITE=="Ghana") %>% select(MOMID, SITE, M08_MAT_VISIT_FORM_COMPLETED_1, M08_LBSTDAT_1, M08_HBA1C_PRCNT_1)

########################################################################################
```

# SUBSET OF VARIABLES THAT MAKE GEST_DIAB_MEAS
```{r}
table(diabetes_df$M08_HBA1C_PRCNT_1, useNA = "always") # has -5 and -7 as NA
# overt diabetes:
diabetes_df <- diabetes_df3 
diabetes_df <- diabetes_df %>% filter(!is.na(M08_LBSTDAT_3)) %>%
  mutate(OVERT_DIA = case_when(M08_HBA1C_PRCNT_1>=6.5 ~ 1,
                               (is.na(M08_HBA1C_PRCNT_1) |
                                  M08_HBA1C_PRCNT_1==-5 |
                                  M08_HBA1C_PRCNT_1==-7) ~ as.numeric(NA),
         TRUE ~ as.numeric(0)))

table(diabetes_df$OVERT_DIA, diabetes_df$SITE, useNA = "always")
round(prop.table(table(diabetes_df$OVERT_DIA, diabetes_df$SITE, useNA = "always"), margin=2)*100,2)

# OGTT: 
diabetes_df <- diabetes_df %>% filter(!is.na(M08_LBSTDAT_3)) %>%
  mutate(OGTT_PRE = case_when(M08_BGLUC_PRETEST_MMOLL_LBORRES_3>=5.1 ~ 1,
                              (is.na(M08_BGLUC_PRETEST_MMOLL_LBORRES_3) |
                                 M08_BGLUC_PRETEST_MMOLL_LBORRES_3==-5 |
                                 M08_BGLUC_PRETEST_MMOLL_LBORRES_3==-7) ~ as.numeric(NA),
         TRUE ~ as.numeric(0)))
table(diabetes_df$OGTT_PRE, diabetes_df$SITE, useNA = "always")
round(prop.table(table(diabetes_df$OGTT_PRE, diabetes_df$SITE, useNA = "always"), margin=2)*100,2)

# OGTT 1-hr: 
diabetes_df <- diabetes_df %>% filter(!is.na(M08_LBSTDAT_3)) %>%
  mutate(OGTT_1hr = case_when(M08_BGLUC_ORAL_1HR_MMOLL_LBORRES_3>=10.0 ~ 1,
                              (is.na(M08_BGLUC_ORAL_1HR_MMOLL_LBORRES_3) |
                                 M08_BGLUC_ORAL_1HR_MMOLL_LBORRES_3==-5 |
                                 M08_BGLUC_ORAL_1HR_MMOLL_LBORRES_3==-7) ~ as.numeric(NA),
         TRUE ~ as.numeric(0))) #%>%
     #filter(OGTT_1hr==1) %>% select(MOMID, OGTT_1hr, M08_BGLUC_ORAL_1HR_MMOLL_LBORRES)
table(diabetes_df$OGTT_1hr, diabetes_df$SITE, useNA = "always")
round(prop.table(table(diabetes_df$OGTT_1hr, diabetes_df$SITE, useNA = "always"), margin=2)*100,2)

# OGTT 2-hr: 
diabetes_df <- diabetes_df %>% filter(!is.na(M08_LBSTDAT_3)) %>%
  mutate(OGTT_2hr = case_when(M08_BGLUC_ORAL_2HR_MMOLL_LBORRES_3 >=8.5 ~ 1,
                              (is.na(M08_BGLUC_ORAL_2HR_MMOLL_LBORRES_3) | 
                                 M08_BGLUC_ORAL_2HR_MMOLL_LBORRES_3==-5 |
                                 M08_BGLUC_ORAL_2HR_MMOLL_LBORRES_3==-7) ~ as.numeric(NA),
         TRUE ~ as.numeric(0)))

table(diabetes_df$OGTT_2hr, diabetes_df$SITE, useNA = "always")
round(prop.table(table(diabetes_df$OGTT_2hr, diabetes_df$SITE, useNA = "always"), margin=2)*100,2)

diabetes_df <- diabetes_df %>%
  mutate(GEST_DIAB_MEAS_TEST = case_when((OVERT_DIA==0 & (OGTT_PRE==1  | OGTT_1hr==1 | OGTT_2hr==1)) ~ 1,
         TRUE ~ as.numeric(0)))
table(diabetes_df$GEST_DIAB_MEAS_TEST, diabetes_df$SITE)
round(prop.table(table(diabetes_df$GEST_DIAB_MEAS_TEST, diabetes_df$SITE, useNA = "always"), margin=2)*100,2)

# RUN THIS WRITE.CSV CODE SO THAT 'MAT_GDM_TABLES.RMD' RUNS
write.csv(diabetes_df, '../data_out/mat_diabetes_fortables.csv') # restricted to women who have a visit 3. 

# temp.df <- diabetes_df %>%
#   select(MOMID, PREGID, SITE, DELIVERED_FF, GEST_DIAB_MEAS, M08_HBA1C_LBORRES_1) %>% filter(SITE=="Pakistan")
#         # M04_DIABETES_EVER_MHOCCUR_3, M04_DIABETES_EVER_MHOCCUR_4, M04_DIABETES_EVER_MHOCCUR_5,
#         # M09_GEST_DIAB_MHOCCUR_6, M09_INDUCED_PROCCUR_6, M09_INDUCED_PRINDC_6,
#         # M19_PRIMARY_MHTERM_13, M19_LD_COMPL_MHTERM_3_13,
        
        # MEASURED VARS:
      #  M06_BGLUC_POC_MMOLL_LBORRES_3, M08_BGLUC_PRETEST_MMOLL_LBORRES_3,
     #   M08_BGLUC_ORAL_1HR_MMOLL_LBORRES_3, M08_BGLUC_ORAL_2HR_MMOLL_LBORRES_3) %>% filter(SITE=="Pakistan")
# write.csv(temp.df, 'data_out/diabetes.temp.csv') # INVESTINGATING!

```

#  DIAGNOISED - OVERT DIABETES
```{r}
# This is DIAGNOSED at enrollment, ANC28, 32, 36 through MNH04.

#tapply(diabetes_df$M08_HBA1C_LBORRES_1, diabetes_df$SITE, summary)
# %>% group_by(SITE) %>% summary(M08_HBA1C_LBORRES_1)
# HAVE YOU EVER BEEN DIAGNOSED WITH DIABETES (PRE-EXISITING OR CHRONIC) NEED FROM VISITS 3,4,5.
diabetes_df3 <- diabetes_df3 %>% 
  mutate(OVERT_DIAB_DIAG = case_when((is.na(M04_DIABETES_EVER_MHOCCUR_3==0) | M04_DIABETES_EVER_MHOCCUR_3==0 | 
                                       is.na(M04_DIABETES_EVER_MHOCCUR_4) | M04_DIABETES_EVER_MHOCCUR_4==0 | 
                                       is.na(M04_DIABETES_EVER_MHOCCUR_5) | M04_DIABETES_EVER_MHOCCUR_5==0) &
                                      ((M09_GEST_DIAB_MHOCCUR_6==1 | # WAS MOTHER DIAGNOSED WITH GDM
                                          (M09_INDUCED_PROCCUR_6==1 & M09_INDUCED_PRINDC_6==8)) |
                                         (M19_PRIMARY_MHTERM_13==4 & M19_LD_COMPL_MHTERM_3_13)) ~ 1,
                                    TRUE ~ as.numeric(0)))

table(OVERT_DIAB_DIAG = diabetes_df3$OVERT_DIAB_DIAG, SITE = diabetes_df3$SITE, useNA = "always")
round(prop.table(table(OVERT_DIAB_DIAG = diabetes_df3$OVERT_DIAB_DIAG, SITE = diabetes_df3$SITE, useNA = "always"), margin=2)*100,2)

```
