---
title: "Vital Signs Analysis"
date: "`r Sys.Date()`"
output:
  pdf_document:
    toc: true
    toc_depth: 3
    latex_engine: xelatex
    keep_tex: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE, out.width = "100%", fig.align = "center") 

library(tidyverse)

load("derived_data/data_vital_long.rda")
load("derived_data/data_bp_long.rda")
load("derived_data/data_fhr_long.rda")

#function for get last digit of integers
lastdigit <- function(x) {
  floor(x -floor(x/10)*10)
}
```
### Includes data from synapse last updated: {.unlisted .unnumbered}
### Ghana : 2023-07-28 {.unlisted .unnumbered}
### Kenya : 2023-08-04 {.unlisted .unnumbered}
### Pakistan : 2023-08-04 {.unlisted .unnumbered}
### Zambia : 2023-07-21 {.unlisted .unnumbered}

\newpage

# Section1. Blood Pressure (BP)

## Figure1.1 Blood Pressure (BP) with High BP threshold by Gestational Age (GA) by Site

```{r}
#plot blood pressure
plot_bp_long <- data_bp_long %>% 
  filter(!is.na(bp) & !is.na(ga_wks)) %>% 
  filter(bp < 200) #!!!temp range

plot_bp_long %>% 
  ggplot(aes(x = ga_wks, y = bp, group = bp_type, color = bp_type)) +
  geom_point(alpha = 0.25, size = 1) +
  geom_hline(aes(yintercept = 90, col= "yellow1"), alpha=0.6, linetype="F1") +
  geom_hline(aes(yintercept = 140,col= "yellow2"), alpha=0.6, linetype="F1") +
  facet_grid(rows = vars(SITE)) + 
  theme_bw() +
  theme(strip.background=element_rect(fill="white")) + 
  theme(axis.text.x = element_text(angle = 60, vjust = 1, hjust=1),
        legend.position="bottom",
        legend.title = element_blank(),
        panel.grid.minor = element_blank()) +
  scale_x_continuous(breaks=seq(floor(min(plot_bp_long$ga_wks)),
    max(plot_bp_long$ga_wks,10)))+
  xlab("Gestational Age (weeks)") +
  ylab("Blood Pressure (mm Hg)") +
  scale_color_manual(
    name="",
    labels=c("Diastolic BP","Systolic BP","High DBP threshold","High SBP threshold"),
    values=c("red3","royalblue3","red3","royalblue3"),
    guide=guide_legend(override.aes = list(
                       linetype=c("blank", "blank","F1","F1"),
                       shape=c(16,16,NA,NA),
                       alpha=0.6)))

```
*Figure1.1 shows the relationship between GA and BP by site. Red line indicates the high DBP threshold at 90 mm Hg. Blue line indicates the high SDP threshold at 140 mm Hg.

## Figure1.2 Blood Pressure (BP) with 95% Confidence Band by Gestational Age (GA) by Site

```{r}
plot_bp_long %>% 
  ggplot(aes(x = ga_wks, y = bp, group = bp_type, color = bp_type)) +
  geom_point(alpha = 0.25, size = 1) +
  geom_smooth(method="loess",  se=TRUE, size = 0.2, span = 0.75, aes(group=bp_type)) + 
  facet_grid(rows = vars(SITE)) + 
  theme_bw() +
  theme(strip.background=element_rect(fill="white")) + 
  theme(axis.text.x = element_text(angle = 60, vjust = 1, hjust=1),
        legend.position="bottom",
        legend.title = element_blank(),
        panel.grid.minor = element_blank()) +
  scale_x_continuous(breaks=seq(floor(min(plot_bp_long$ga_wks)),
    max(plot_bp_long$ga_wks,10)))+
  xlab("Gestational Age (weeks)") +
  ylab("Blood Pressure (mm Hg)") +
  scale_color_manual(
    name="",
    labels=c("Diastolic BP","Systolic BP"),
    values=c("red3","royalblue3"),
    guide=guide_legend(override.aes = list(alpha=0.6)))

```

*Figure1.2 shows the relationship between GA and BP by site, also shows the mean and 95% confidence band of BP at different GA by fitting a local polynomial regression model for each site.

## Figure1.3 Blood Pressure (BP) Site Comparison by Gestational Age (GA) 

```{r}
plot_bp_long %>% 
  ggplot(aes(x = ga_wks, y = bp, group = interaction(bp_type,SITE), color =interaction(bp_type,SITE))) + geom_smooth(method="loess",  se=TRUE, size = 0.8, span = 0.75) + 
  theme_bw() +
  theme(strip.background=element_rect(fill="white")) + 
  theme(axis.text.x = element_text(angle = 60, vjust = 1, hjust=1),
        legend.position="bottom",
        legend.title = element_blank(),
        panel.grid.minor = element_blank()) +
  scale_x_continuous(breaks=seq(floor(min(plot_bp_long$ga_wks)),
    max(plot_bp_long$ga_wks,10)))+
  xlab("Gestational Age (weeks)") +
  ylab("Blood Pressure (mm Hg)") +
  scale_color_manual(values = c("red", "red4", "blue", "blue4", "green", "green4", "orange", "orange4"))
  # scale_color_brewer(palette="Set1")

```

*Figure1.3 shows the site difference/similarity of the mean and 95% confidence band of BP at different GA fitted by the local polynomial regression model.

## Figure1.4 Blood Pressure (BP) Digit Preference Site Comparison

```{r}
plot_bp_digit <- plot_bp_long %>% 
  mutate(digit = lastdigit(bp))
  
#Systolic
plot_sbp_digit <- plot_bp_digit %>% 
  filter(bp_type == "Systolic") 

plot_sbp_digit %>%
  ggplot(aes(x = digit)) +
    geom_histogram(binwidth = 1, fill = "royalblue3", color = "black", alpha = 0.6) + 
  labs(title = "Systolic Digit Preference", 
       x = "Digit",   
       y = "Frequency") + scale_x_continuous(breaks = seq(0, 10, by = 1), labels = seq(0, 10, by = 1)) +
  facet_grid(rows = vars(SITE), scales = "free_y") +
  theme_bw() +  
  theme(axis.text.x = element_text(angle = 0, vjust = 1, hjust=1),
        legend.position="bottom",
        panel.grid.minor = element_blank()) +
     theme(strip.background=element_rect(fill="white")) 

#Diastolic
plot_dbp_digit <- plot_bp_digit %>% 
  filter(bp_type == "Diastolic") 

plot_dbp_digit %>%
  ggplot(aes(x = digit)) +
    geom_histogram(binwidth = 1, fill = "red3", color = "black", alpha = 0.6) + 
  labs(title = "Diastolic Digit Preference", 
       x = "Digit",   
       y = "Frequency") + scale_x_continuous(breaks = seq(0, 10, by = 1), labels = seq(0, 10, by = 1)) +
  facet_grid(rows = vars(SITE), scales = "free_y") +
  theme_bw() +  
  theme(axis.text.x = element_text(angle = 0, vjust = 1, hjust=1),
        legend.position="bottom",
        panel.grid.minor = element_blank()) +
   theme(strip.background=element_rect(fill="white")) 

```
*Figure 1.4 shows the digit preference histograms for Systolic and Diastolic BP measurement by site.

\newpage

# Section2. Body Temperature

## Figure2.1 Body Temperature with 95% Confidence Band by Gestational Age (GA) by Site

```{r}
#plot vital status
plot_temperature <- data_vital_long %>% 
  select(SCRNID, MOMID, PREGID, SITE, ga_wks, TEMP_VSORRES) %>% 
  filter(!is.na(TEMP_VSORRES) & !is.na(ga_wks)) %>% 
  filter(TEMP_VSORRES >= 30 & TEMP_VSORRES <= 42) #remove outliers

plot_temperature %>% 
  ggplot(aes(x = ga_wks, y = TEMP_VSORRES)) +
  geom_point(alpha = 0.25, color = "royalblue3", size = 1) +
  geom_smooth(method="loess",  se=TRUE, size = 0.2, span = 0.75, aes(color="coral")) +
  scale_x_continuous(breaks=seq(
    floor(min(plot_temperature$ga_wks)),
    max(plot_temperature$ga_wks,5)))+
  xlab("Gestational Age (weeks)") +
  ylab("Temperature (Celsius)") + 
  facet_grid(rows = vars(SITE)) +
  theme_bw() +  
  theme(axis.text.x = element_text(angle = 60, vjust = 1, hjust=1),
        legend.position="bottom",
        panel.grid.minor = element_blank()) +
  theme(strip.background=element_rect(fill="white"))+
  scale_color_identity(name = "", breaks=c("royalblue3","coral"),guide = 'legend',
                       labels = c("Temperature",'Fitted mean with 95% confidence band'))

```

*Figure2.1 shows the relationship between GA and body temperature by site, also shows the mean and 95% confidence band of body temperature at different GA by fitting a local polynomial regression model for each site.

## Figure2.2 Body Temperature Site Comparison by Gestational Age (GA) 

```{r}
plot_temperature %>% 
  ggplot(aes(x = ga_wks, y = TEMP_VSORRES, group=SITE, color=SITE)) +
  geom_smooth(method="loess",  se=TRUE, size = 0.8, span = 0.75) +
  scale_x_continuous(breaks=seq(
    floor(min(plot_temperature$ga_wks)),
    max(plot_temperature$ga_wks,5)))+
  xlab("Gestational Age (weeks)") +
  ylab("Temperature (Celsius)") + 
  theme_bw() +  
  theme(axis.text.x = element_text(angle = 60, vjust = 1, hjust=1),
        legend.position="bottom",
        panel.grid.minor = element_blank()) +
  theme(strip.background=element_rect(fill="white"))+
  scale_color_brewer(palette="Set2")

```

*Figure2.2 shows the site difference/similarity of the mean and 95% confidence band of body temperature at different GA fitted by the local polynomial regression model.

## Figure2.3 Body Temperature Digit Preference Site Comparison
```{r}
plot_tempe_digit <- plot_temperature %>% 
  mutate(digit = round(TEMP_VSORRES, 1) - floor(round(TEMP_VSORRES, 1)))

plot_tempe_digit %>%
  ggplot(aes(x = digit)) +
    geom_histogram(binwidth = 0.1, fill = "royalblue3", color = "black", alpha = 0.6) + 
  labs(title = "", 
       x = "Digit",   
       y = "Frequency") + scale_x_continuous(breaks = seq(0, 1, by = 0.1), labels = seq(0, 1, by = 0.1)) +
  facet_grid(rows = vars(SITE), scales = "free_y") +
  theme_bw() +  
   theme(strip.background=element_rect(fill="white")) 

```
*Figure 2.3 shows the digit preference histograms for temperature measurement by site.

\newpage

# Section3. Maternal Heart Rate (MHR)

## Figure3.1 Maternal Heart Rate (MHR) with 95% Confidence Interval (CI) by Gestational Age (GA) by Site

```{r}
#plot vital status
plot_mhr <- data_vital_long %>% 
  select(SCRNID, MOMID, PREGID, SITE, ga_wks, MHR_VSORRES) %>% 
  filter(!is.na(MHR_VSORRES) & !is.na(ga_wks)) %>% 
  filter(MHR_VSORRES >= 40 & MHR_VSORRES <= 170) 

plot_mhr_overall <- plot_mhr %>% group_by(SITE) %>% 
  summarise(
    mean=mean(MHR_VSORRES),
    sd1_above=mean+sd(MHR_VSORRES),
    sd1_below=mean-sd(MHR_VSORRES),
    sd2_above=mean+2*sd(MHR_VSORRES),
    sd2_below=mean-2*sd(MHR_VSORRES))

plot_mhr %>% 
  ggplot(aes(x = ga_wks, y = MHR_VSORRES)) +
  geom_point(alpha = 0.25, color = "red3", size = 1) +
  geom_hline(data = plot_mhr_overall, 
             aes(yintercept = sd2_above, col= "deepskyblue3"), alpha=0.6, linetype="dashed") +
  geom_hline(data = plot_mhr_overall, 
             aes(yintercept = mean, col= "blue"), alpha=0.6) +
  geom_hline(data = plot_mhr_overall, 
             aes(yintercept = sd2_below, col= "deepskyblue3"), alpha=0.6, linetype="dashed") +
  scale_x_continuous(breaks=seq(
    floor(min(plot_mhr$ga_wks)),
    max(plot_mhr$ga_wks,5)))+
  xlab("Gestational Age (weeks)") +
  ylab("Maternal Heart Rate (beats per minutes)") + 
  facet_grid(rows = vars(SITE)) +
  theme_bw() +  
  theme(axis.text.x = element_text(angle = 60, vjust = 1, hjust=1),
        legend.position="bottom",
        panel.grid.minor = element_blank()) +
  theme(strip.background=element_rect(fill="white")) +
  scale_color_manual(name="MHR",values=c("blue","deepskyblue3"), labels=c("Mean", "95% CI"))+
  guides(colour = guide_legend(override.aes = list(alpha = c(0.6,0.3), 
                                                   linetype=c("solid", "dashed"))))
```

*Figure3.1 shows the relationship between GA and MHR by site. The lines show the overall mean and 95% CI of MHR during the pregnancy at each site.


## Figure3.2 Maternal Heart Rate (MHR) with 95% Confidence Band by Gestational Age (GA) by Site

```{r}
plot_mhr_mean <- plot_mhr %>% group_by(ga_wks, SITE) %>% summarise(MHR_VSORRES=mean(MHR_VSORRES))

plot_mhr %>% 
  ggplot(aes(x = ga_wks, y = MHR_VSORRES)) +
  geom_point(alpha = 0.25, color = "red3", size = 1) +
  geom_smooth(method="loess",  se=TRUE, size = 0.2, span = 0.75, aes(color="deepskyblue3")) +
  scale_x_continuous(breaks=seq(
    floor(min(plot_mhr$ga_wks)),
    max(plot_mhr$ga_wks,5)))+
  xlab("Gestational Age (weeks)") +
  ylab("Maternal Heart Rate (beats per minutes)") + 
  facet_grid(rows = vars(SITE)) +
  theme_bw() +  
  theme(axis.text.x = element_text(angle = 60, vjust = 1, hjust=1),
        legend.position="bottom",
        panel.grid.minor = element_blank()) +
  theme(strip.background=element_rect(fill="white")) +
  scale_color_identity(name = "", breaks="deepskyblue3",guide = 'legend',labels = c('Fitted mean with 95% confidence band'))

```
*Figure3.2 shows the relationship between GA and MHR by site, also shows the mean and 95% confidence band of MHR at different GA by fitting a local polynomial regression model for each site.


## Figure3.3 Maternal Heart Rate (MHR) Site Comparison by Gestational Age

```{r}
plot_mhr %>% 
  ggplot(aes(x = ga_wks, y = MHR_VSORRES, group=SITE, color=SITE)) +
  geom_smooth(method="loess",  se=TRUE, size = 0.8, span = 0.75) +
  scale_x_continuous(breaks=seq(
    floor(min(plot_mhr$ga_wks)),
    max(plot_mhr$ga_wks,5)))+
  xlab("Gestational Age (weeks)") +
  ylab("Maternal Heart Rate (beats per minutes)") + 
  theme_bw() +  
  theme(axis.text.x = element_text(angle = 60, vjust = 1, hjust=1),
        legend.position="bottom",
        panel.grid.minor = element_blank()) +
  theme(strip.background=element_rect(fill="white")) +
  scale_color_brewer(palette="Set1")

```
*Figure3.3 shows the site difference/similarity of the mean and 95% confidence band of MHR at different GA fitted by the local polynomial regression model.

## Figure3.4 Maternal Heart Rate (MHR) Digit Preference Site Comparison
```{r}
plot_mhr_digit <- plot_mhr %>% 
  mutate(digit = lastdigit(MHR_VSORRES))

plot_mhr_digit %>%
  ggplot(aes(x = digit)) +
    geom_histogram(binwidth = 1, fill = "red3", color = "black", alpha = 0.6) + 
  labs(title = "", 
       x = "Digit",   
       y = "Frequency") + scale_x_continuous(breaks = seq(0, 10, by = 1), labels = seq(0, 10, by = 1)) +
  facet_grid(rows = vars(SITE), scales = "free_y") +
  theme_bw() +  
   theme(strip.background=element_rect(fill="white")) 

```
*Figure 3.4 shows the digit preference histograms for maternal heart rate measurement by site.

\newpage

# Section4. Respiratory Rate (RR)

## Figure4.1 Respiratory Rate (RR) with 95% Confidence Band by Gestational Age (GA) by Site

```{r}
#plot vital status
plot_rr <- data_vital_long %>% 
  select(SCRNID, MOMID, PREGID, SITE, ga_wks, RR_VSORRES) %>% 
  filter(!is.na(RR_VSORRES) & !is.na(ga_wks)) %>% 
  filter(RR_VSORRES >=5 & RR_VSORRES <= 40) #remove outliers

plot_rr %>% 
  ggplot(aes(x = ga_wks, y = RR_VSORRES)) +
  geom_point(alpha = 0.25, color = "darkgreen", size = 1) +
    geom_smooth(method="loess",  se=TRUE, size = 0.2, span = 0.75, aes(color="palevioletred")) +
  scale_x_continuous(breaks=seq(
    floor(min(plot_rr$ga_wks)),
    max(plot_rr$ga_wks,5)))+
  xlab("Gestational Age (weeks)") +
  ylab("Respiratory Rate (breaths per minutes)") + 
  facet_grid(rows = vars(SITE)) +
  theme_bw() +  
  theme(axis.text.x = element_text(angle = 60, vjust = 1, hjust=1),
        legend.position="bottom",
        panel.grid.minor = element_blank()) +
  theme(strip.background=element_rect(fill="white")) +
  scale_color_identity(name = "", breaks="palevioletred",guide = 'legend',
                       labels = c('Fitted mean with 95% confidence band'))
```

*Figure4.1 shows the relationship between gestational age and respiratory rate by site, also shows the mean and 95% confidence band of respiratory rate at different gestational age by fitting a local polynomial regression model for each site.

## Figure4.2 Respiratory Rate (RR) Site Comparison by Gestational Age (GA)

```{r}
plot_rr %>% 
  ggplot(aes(x = ga_wks, y = RR_VSORRES, group=SITE, color=SITE)) +
    geom_smooth(method="loess",  se=TRUE, size = 0.8, span = 0.75) +
  scale_x_continuous(breaks=seq(
    floor(min(plot_rr$ga_wks)),
    max(plot_rr$ga_wks,5)))+
  xlab("Gestational Age (weeks)") +
  ylab("Respiratory Rate (breaths per minutes)") + 
  theme_bw() +  
  theme(axis.text.x = element_text(angle = 60, vjust = 1, hjust=1),
        legend.position="bottom",
        panel.grid.minor = element_blank()) +
  theme(strip.background=element_rect(fill="white")) +
  scale_color_brewer(palette="Set2")
```

*Figure4.2 shows the site difference/similarity of the mean and 95% confidence band of RR at different GA fitted by the local polynomial regression model.

## Figure4.3 Respiratory Rate (RR) Digit Preference Site Comparison
```{r}
plot_rr_digit <- plot_rr %>% 
  mutate(digit = lastdigit(RR_VSORRES))

plot_rr_digit %>%
  ggplot(aes(x = digit)) +
    geom_histogram(binwidth = 1, fill = "darkgreen", color = "black", alpha = 0.6) + 
  labs(title = "", 
       x = "Digit",   
       y = "Frequency") + scale_x_continuous(breaks = seq(0, 10, by = 1), labels = seq(0, 10, by = 1)) +
  facet_grid(rows = vars(SITE), scales = "free_y") +
  theme_bw() +  
   theme(strip.background=element_rect(fill="white")) 

```
*Figure 4.3 shows the digit preference histograms for respiratory rate measurement by site.
\newpage

# Section5. Oxygen Saturation (SpO2)

## Figure5.1 Oxygen Saturation (SpO2) by with 95% Confidence Band Gestational Age (GA) by Site

```{r}
#plot vital status
plot_spo2 <- data_vital_long %>% 
  select(SCRNID, MOMID, PREGID, SITE, ga_wks, PULSEOX_VSORRES) %>% 
  filter(!is.na(PULSEOX_VSORRES) & !is.na(ga_wks)) %>% 
  filter(PULSEOX_VSORRES >= 85 & PULSEOX_VSORRES <= 100)

plot_spo2 %>% 
  ggplot(aes(x = ga_wks, y = PULSEOX_VSORRES)) +
    geom_point(alpha = 0.25, color = "darkblue", size = 0.8) +
  geom_smooth(method="loess",  se=TRUE, size = 0.2, span = 0.75, aes(color="darkorange1")) +
  scale_x_continuous(breaks=seq(
    floor(min(plot_spo2$ga_wks)),
    max(plot_spo2$ga_wks,5)))+
  xlab("Gestational Age (weeks)") +
  ylab("oxygen Saturation (%)") + 
  facet_grid(rows = vars(SITE)) +
  theme_bw() +  
  theme(axis.text.x = element_text(angle = 60, vjust = 1, hjust=1),
        legend.position="bottom",
        panel.grid.minor = element_blank()) +
  theme(strip.background=element_rect(fill="white"))+
  scale_color_identity(name = "", breaks="darkorange1",guide = 'legend',
                       labels = c('Fitted mean with 95% confidence band'))
```

*Figure5.1 shows the relationship between gestational age and oxygen saturation by site, also shows the mean and 95% confidence band of oxygen saturation at different gestational age by fitting a local polynomial regression model for each site.

## Figure5.2 Oxygen Saturation (SpO2) Site Comparison by Gestational Age (GA)

```{r}
plot_spo2 %>% 
  ggplot(aes(x = ga_wks, y = PULSEOX_VSORRES, group=SITE, color=SITE)) +
  geom_smooth(method="loess",  se=TRUE, size = 0.8, span = 0.75) +
  scale_x_continuous(breaks=seq(
    floor(min(plot_spo2$ga_wks)),
    max(plot_spo2$ga_wks,5)))+
  xlab("Gestational Age (weeks)") +
  ylab("oxygen Saturation (%)") + 
  theme_bw() +  
  theme(axis.text.x = element_text(angle = 60, vjust = 1, hjust=1),
        legend.position="bottom",
        panel.grid.minor = element_blank()) +
  theme(strip.background=element_rect(fill="white"))+
  scale_color_brewer(palette="Dark2")
```

*Figure5.2 shows the site difference/similarity of the mean and 95% confidence band of SpO2 at different GA fitted by the local polynomial regression model.

## Figure5.3 Oxygen Saturation (SpO2)) Digit Preference Site Comparison
```{r}
#plot
plot_spo2_digit <- plot_spo2 %>% 
  mutate(digit = lastdigit(PULSEOX_VSORRES))

plot_spo2_digit %>%
  ggplot(aes(x = digit)) +
    geom_histogram(binwidth = 1, fill = "darkblue", color = "black", alpha = 0.6) + 
  labs(title = "", 
       x = "Digit",   
       y = "Frequency") + scale_x_continuous(breaks = seq(0, 10, by = 1), labels = seq(0, 10, by = 1)) +
  facet_grid(rows = vars(SITE), scales = "free_y") +
  theme_bw() +  
   theme(strip.background=element_rect(fill="white")) 

```
*Figure 5.3 shows the digit preference histograms for oxygen saturation measurement by site.


\newpage

# Section6. Pallor

## Figure6. Sign of Pallor by Gestational Age (GA)by Site

```{r}
#define data
plot_pallor <- data_vital_long %>% 
  select(SCRNID, MOMID, PREGID, SITE, ga_wks, PALLOR_VSORRES) %>% 
  filter(!is.na(PALLOR_VSORRES) & !is.na(ga_wks) & PALLOR_VSORRES != 8) 
  
plot_pallor$PALLOR_VSORRES <- factor(
  plot_pallor$PALLOR_VSORRES, 
  levels = c(99, 0, 1),
  labels = c("Don't know", "No sign of pallor", "Show sign of pallor"))

plot_pallor %>% 
  ggplot(aes(x = floor(ga_wks), fill = PALLOR_VSORRES)) +
  geom_histogram( color = "black", linewidth = 0.1,
                 alpha= 0.8, position= "fill", binwidth = 1) +
  scale_fill_manual(values = c("mediumpurple1", "cadetblue1", "orange")) +
  scale_x_continuous(breaks=seq(
    floor(min(plot_pallor$ga_wks)),
    max(plot_pallor$ga_wks,1)))+
  xlab("Gestational Weeks") +
  ylab("Percentage") + 
  facet_grid(rows = vars(SITE), scales = "free_y") +
  theme_bw() +  
  theme(axis.text.x = element_text(angle = 60, vjust = 1, hjust=1),
        legend.position="bottom",
        panel.grid.minor = element_blank()) +
  guides(fill=guide_legend(title="",reverse=TRUE))


```

*Figure6. shows the distribution of sign of pallor by GA by site.

\newpage

# Section7. Non-invasive Total Hemoglobin (SpHb)

## Figure7.1 Non-invasive Total Hemoglobin (SpHb) with 95% Confidence Band by Gestational Age (GA) by Site

```{r}
#plot vital status
plot_sphb <- data_vital_long %>% 
  select(SCRNID, MOMID, PREGID, SITE, ga_wks, SPHB_LBORRES) %>% 
  filter(!is.na(SPHB_LBORRES) & !is.na(ga_wks)) %>% 
  filter(SPHB_LBORRES >=1 & SPHB_LBORRES <= 20 ) #remove outliers
  
plot_sphb %>% 
  ggplot(aes(x = ga_wks, y = SPHB_LBORRES)) +
  geom_point(alpha = 0.25, color = "indianred1", size = 1) +
  geom_smooth(method="loess",  se=TRUE, size = 0.2, span = 0.75, aes(color="royalblue2")) +
  scale_x_continuous(breaks=seq(
    floor(min(plot_sphb$ga_wks)),
    max(plot_sphb$ga_wks,5)))+
  xlab("Gestational Age (weeks)") +
  ylab("Non-invasive Total Hemoglobin (SpHb) (g/dL)") + 
  facet_grid(rows = vars(SITE)) +
  theme_bw() +  
  theme(axis.text.x = element_text(angle = 60, vjust = 1, hjust=1),
        legend.position="bottom",
        panel.grid.minor = element_blank()) +
  theme(strip.background=element_rect(fill="white"))+
  scale_color_identity(name = "", breaks="royalblue2",guide = 'legend',
                       labels = c('Fitted mean with 95% confidence band'))

```

*Figure7.1 shows the relationship between GA and SpHb by site, also shows the mean and 95% confidence band of SpHb at different GA by fitting a local polynomial regression model for each site.

## Figure7.2 Non-invasive Total Hemoglobin (SpHb) Site Comparison by Gestational Age (GA)

```{r}
plot_sphb %>% 
  ggplot(aes(x = ga_wks, y = SPHB_LBORRES, group=SITE, color=SITE)) +
  geom_smooth(method="loess",  se=TRUE, size = 0.8, span = 0.75) +
  scale_x_continuous(breaks=seq(
    floor(min(plot_sphb$ga_wks)),
    max(plot_sphb$ga_wks,5)))+
  xlab("Gestational Age (weeks)") +
  ylab("Non-invasive Total Hemoglobin (SpHb) (g/dL)") + 
  theme_bw() +  
  theme(axis.text.x = element_text(angle = 60, vjust = 1, hjust=1),
        legend.position="bottom",
        panel.grid.minor = element_blank()) +
  theme(strip.background=element_rect(fill="white"))+
  scale_color_brewer(palette="Set1")

```

*Figure7.2 shows the site difference/similarity of the mean and 95% confidence band of SpHb at different GA fitted by the local polynomial regression model.

## Figure7.3 SpHb Digit Preference Site Comparison
```{r}
plot_sphb_digit <- plot_sphb %>% 
  mutate(digit = round(SPHB_LBORRES, 1) - floor(round(SPHB_LBORRES, 1)))

plot_sphb_digit %>%
  ggplot(aes(x = digit)) +
    geom_histogram(binwidth = 0.1, fill = "indianred1", color = "black", alpha = 0.6) + 
  labs(title = "", 
       x = "Digit",   
       y = "Frequency") + scale_x_continuous(breaks = seq(0, 1, by = 0.1), labels = seq(0, 1, by = 0.1)) +
  facet_grid(rows = vars(SITE), scales = "free_y") +
  theme_bw() +  
   theme(strip.background=element_rect(fill="white")) 

```
*Figure 7.3 shows the digit preference histograms for SpHb measurement by site.
\newpage

# Section8. Fetal Heart Rate (FHR)

## Figure8.1 Fetal Heart Rate (FHR) with 95% Confidence Band by Gestational Age (GA) by Site

```{r}
#plot vital status
plot_fhr <- data_fhr_long %>% 
  select(SCRNID, MOMID, PREGID, SITE, ga_wks, fhr) %>% 
  filter(!is.na(fhr) & !is.na(ga_wks)) %>% 
  filter(fhr >= 60 & fhr <= 190)

plot_fhr %>% 
  ggplot(aes(x = ga_wks, y = fhr)) +
    geom_point(alpha = 0.25, color = "red3", size = 1) +
  geom_smooth(method="loess",  se=TRUE, size = 0.2, span = 0.75, aes(color="seagreen")) +
  scale_x_continuous(breaks=seq(
    floor(min(plot_fhr$ga_wks)),
    max(plot_fhr$ga_wks,5)))+
  xlab("Gestational Age (weeks)") +
  ylab("Fetal Heart Rate (FHR) (beats per minute)") + 
  facet_grid(rows = vars(SITE)) +
  theme_bw() +  
  theme(axis.text.x = element_text(angle = 60, vjust = 1, hjust=1),
        legend.position="bottom",
        panel.grid.minor = element_blank()) +
  theme(strip.background=element_rect(fill="white"))+
  scale_color_identity(name = "", breaks="seagreen",guide = 'legend',
                       labels = c('Fitted mean with 95% confidence band'))
```

*Figure8.1 shows the relationship between GA and FHR by site, also shows the mean and 95% confidence band of FHR at different GA by fitting a local polynomial regression model for each site.

## Figure8.2 Fetal Heart Rate (FHR) Site Comparison by Gestational Age (GA)

```{r}
plot_fhr %>% 
  ggplot(aes(x = ga_wks, y = fhr, group=SITE, color=SITE)) +
  geom_smooth(method="loess",  se=TRUE, size = 0.8, span = 0.75) +
  scale_x_continuous(breaks=seq(
    floor(min(plot_fhr$ga_wks)),
    max(plot_fhr$ga_wks,5)))+
  xlab("Gestational Age (weeks)") +
  ylab("Fetal Heart Rate (FHR) (beats per minute)") + 
  theme_bw() +  
  theme(axis.text.x = element_text(angle = 60, vjust = 1, hjust=1),
        legend.position="bottom",
        panel.grid.minor = element_blank()) +
  theme(strip.background=element_rect(fill="white"))+
  scale_color_brewer(palette="Set2")
```

*Figure8.2 shows the site difference/similarity of the mean and 95% confidence band of FHR at different GA fitted by the local polynomial regression model.


## Figure8.3 Fetal Heart Rate (FHR) Digit Preference Site Comparison
```{r}
plot_fhr_digit <- plot_fhr %>% 
  mutate(digit = lastdigit(fhr))

plot_fhr_digit %>%
  ggplot(aes(x = digit)) +
    geom_histogram(binwidth = 1, fill = "red3", color = "black", alpha = 0.6) + 
  labs(title = "", 
       x = "Digit",   
       y = "Frequency") + scale_x_continuous(breaks = seq(0, 10, by = 1), labels = seq(0, 10, by = 1)) +
  facet_grid(rows = vars(SITE), scales = "free_y") +
  theme_bw() +  
   theme(strip.background=element_rect(fill="white")) 

```
*Figure 8.4 shows the digit preference histograms for fetal heart rate measurement by site.
